Week 3 Assignment

### 2018-09-11 DATA607/Week_3_Assignment.Rmd
More work on DATA 607 Wee_3_Assignment.Rmd

(a) [0-9]+\\$
(b) \\b[a-z]{1,4}\\b
(c) .*?\\.txt$
(d) \\d{2}/\\d{2}/\\d{4}
(e) <(.+?)>.+?</\\1>

>>>>

| Question | Regular Expression | Type of String | Examples |
|----------|--------------------|----------------|----------|
| (a) | [0-9]+\\$ | Numbers followed by a dollar sign| 100$, 25$ |
| (b) | \\b[a-z]{1,4}\\b | A one to four lower-case character string  | help, bat | 
| (c) | .*?\\.txt$ | Alphanumeric characters followed by .txt | readme.txt, 1.txt |
| (d) | \\d{2}/\\d{2}/\\d{4} | A date in a DD/MM/YYYY or MM/DD/YYYY format | 12/31/2018 |
| (e) | <(.+?)>.+?</\\1> | Text between to HTML tags | `<b>This is bold</b>` |
